Comparing Different Planned Missingness Designs in Longitudinal Studies

### 2018-05-29 Documentation/manuscript.Rnw
Fixed the hard coded path problem.

@@

<<primary, echo=FALSE, message=FALSE, warning=FALSE, fig.pos = "H">>=
library(kableExtra)
library(dplyr)
load("~/GitHub/designedmissingness/Results/tables20180509_60_1_high_hightime0.RData")
high <- d

load("~/GitHub/designedmissingness/Results/tables20180509_60_1_med_hightime0.RData")
med <- d

load("~/GitHub/designedmissingness/Results/tables20180509_60_1_low_hightime0.RData")
low <- d

@@

<<sampsize, echo=FALSE, message=FALSE, warning=FALSE, fig.pos = "H">>=
library(kableExtra)
library(dplyr)
load("~/GitHub/designedmissingness/Results/tables20180509_120_1_high_hightime0.RData")
high <- d

load("~/GitHub/designedmissingness/Results/tables20180509_120_1_med_hightime0.RData")
med <- d

load("~/GitHub/designedmissingness/Results/tables20180509_120_1_low_hightime0.RData")
low <- d

@@

<<hightime, echo=FALSE, message=FALSE, warning=FALSE, fig.pos = "H">>=
library(kableExtra)
library(dplyr)
load("~/GitHub/designedmissingness/Results/tables20180509_60_1_high_hightime1.RData")
high <- d

load("~/GitHub/designedmissingness/Results/tables20180509_60_1_med_hightime1.RData")
med <- d

load("~/GitHub/designedmissingness/Results/tables20180509_60_1_low_hightime1.RData")
low <- d

@@

<<lowcorr, echo=FALSE, message=FALSE, warning=FALSE, fig.pos = "H">>=
library(kableExtra)
library(dplyr)
load("~/GitHub/designedmissingness/Results/tables20180509_60_0.5_high_hightime0.RData")
high <- d

load("~/GitHub/designedmissingness/Results/tables20180509_60_0.5_med_hightime0.RData")
med <- d

load("~/GitHub/designedmissingness/Results/tables20180509_60_0.5_low_hightime0.RData")
low <- d

>>>>

<<echo=FALSE>>=
if (Sys.info()["user"] == "gregorymatthews") {
  root <- "/Users/gregorymatthews/Dropbox/designedMissingnessGit/Results/"
}

if (Sys.info()["user"] != "gregorymatthews") {
  root <- "~/GitHub/designedmissingness/Results/"
}
@

@@

<<primary, echo=FALSE, message=FALSE, warning=FALSE, fig.pos = "H">>=

library(kableExtra)
library(dplyr)
load(paste0(root,"tables20180509_60_1_high_hightime0.RData"))
high <- d

load(paste0(root,"tables20180509_60_1_med_hightime0.RData"))
med <- d

load(paste0(root,"tables20180509_60_1_low_hightime0.RData"))
low <- d

@@

<<sampsize, echo=FALSE, message=FALSE, warning=FALSE, fig.pos = "H">>=
library(kableExtra)
library(dplyr)
load(paste0(root,"tables20180509_120_1_high_hightime0.RData"))
high <- d

load(paste0(root,"tables20180509_120_1_med_hightime0.RData"))
med <- d

load(paste0(root,"tables20180509_120_1_low_hightime0.RData"))
low <- d

@@

<<hightime, echo=FALSE, message=FALSE, warning=FALSE, fig.pos = "H">>=
library(kableExtra)
library(dplyr)
load(paste0(root,"tables20180509_60_1_high_hightime1.RData"))
high <- d

load(paste0(root,"tables20180509_60_1_med_hightime1.RData"))
med <- d

load(paste0(root,"tables20180509_60_1_low_hightime1.RData"))
low <- d

@@

<<lowcorr, echo=FALSE, message=FALSE, warning=FALSE, fig.pos = "H">>=
library(kableExtra)
library(dplyr)
load(paste0(root,"tables20180509_60_0.5_high_hightime0.RData"))
high <- d

load(paste0(root,"tables20180509_60_0.5_med_hightime0.RData"))
med <- d

load(paste0(root,"tables20180509_60_0.5_low_hightime0.RData"))
low <- d
